---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "The Relationship Between Biomarkers and Exposure of Ozone and PM2.5"
subtitle: "https://github.com/XiangtianWang/EDA_Project.git"
author: "Xiangtian Wang"
fontsize: 12pt
mainfont: Times New Roman

---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
# Set your working directory
getwd()
# Load your packages
library(tidyverse)
library(nlme)
# Set your ggplot theme
mytheme <- theme_classic(base_size = 14) +
  theme(axis.text = element_text(color = "black"), 
        legend.position = "top")
theme_set(mytheme)
# Load your datasets

```
```{r}
# Gather the data
changsha.spread <- gather(Changsha.data,"biomarker", "concentration", ohdg.a : HEHE , na.rm = TRUE)

changsha.gather <- gather(changsha.spread,"exposure", "level", o3exp.12h.x : so2exp.2w.x ,na.rm = TRUE)
colnames(changsha.gather)
d.changsha <- changsha.gather %>%
    mutate( d.conc = concentration[visit ==1])
changsha <- changsha.gather %>%
  dplyr::select(id, visit, group, biomarker, concentration, exposure, level)

d.diff <- changsha %>%
  group_by(id) %>%
  mutate(diff.conc = concentration - concentration[visit = 1])%>%
  mutate(diff.expo = level - level[visit = 1])

# Rationale and Research Questions



\newpage

# Dataset Information



\newpage

# Exploratory Analysis 



\newpage

# Analysis



## Question 1: <insert specific question here and add additional subsections for additional questions below, if needed>

## Question 2: 




\newpage

# Summary and Conclusions


\newpage

# References
<add references here if relevant, otherwise delete this section> 
